Modelling the City of Melbourne Pedestrian Data

### 2017-09-30 presentation/final.Rmd
added slide about prediction - maybe need to say future work, or present a basic initial prediction model

>>>>

# Predictive model using imputed data
- can perform analysis at all locations now with complete data
```{r, echo = FALSE, fig.retina = 6, message=FALSE, warning=F, fig.width = 10, fig.height = 3}
melb_cent_mon9 <- dfa2 %>%
  filter(Day == "Monday",
         Time == 9) %>%
         .$`Melbourne Central`

monday_hdays <- dfa2 %>%
  filter(Day == "Monday",
         Time == 9) %>%
  .$IsHDay

p1 <- ggplot() + geom_line(aes(x = 1:length(melb_cent_mon9),
                             y = melb_cent_mon9)) +
      theme_minimal() + xlab("Time (nth Week since 2014)") +
      geom_point(aes(x = 1:length(melb_cent_mon9),
                     y = 0, alpha = monday_hdays),
                 size = 3) + 
      scale_alpha_discrete(name = "Is public holiday") + 
      ylab("Counts at Monday 9am")
p2 <- ggplot() + geom_density(aes(x = melb_cent_mon9)) +
                 theme_minimal() + xlab("Counts at Monday 9am")

grid.arrange(p1, p2, nrow = 1, top = "Monday 9am Counts at Melbourne Central")

```
- can treat each specific hour of the week as a time series
  * find covariates outside the counts data to help predict counts
  * eg. weather data, public events
